Modern Physics Laser Scanning Project

### 2016-06-18 paper/paper.tex
another update
christine found a grammer error

\begin{abstract}
This experiment was conducted in the Modern Physics class of 2016 at Stuyvesant High School. The goal was to build a laser scanner using a laser and a photodiode and find the maximum achievable resolution of the apparatus.
\end{abstract}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=10cm,height=6cm]{setup_picture}
  \caption[caption]{3D printed components\footnotemark}
\end{figure}
\footnotetext{CADs available here:\cite{github}}

>>>>

\begin{abstract}
This experiment was conducted in the Modern Physics class of 2016 at Stuyvesant High School. The goal was to build a laser scanner using a laser and a photometer to find its maximum achievable resolution.
\end{abstract}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=8cm,height=10cm]{setup_picture}
  \caption[caption]{3D printed components\footnotemark}
\end{figure}
\footnotetext{CADs available here:\cite{github}}
